### 2015-03-02 fundamentals/impl.tex
since the lowercasing of acronyms, it's hard to use their full form at the start of a sentence. I hackily have done this manually for CI in this case..

\emph{\acrfull{CI}} is the idea that software should be tested and validated
as it is being developed, rather than as a final stage in a longer development
cycle.  Under \gls{CI}, every pull request (proposed code change) is tested independently immediately after
it is proposed. Such tests are run on all officially supported platforms.
\Cyclus uses a \gls{CI} platform called Polyphemus
\cite{scopatz_polyphemus_2014}. Polyphemus serves as an intermediary between GitHub pull requests on the front-end
and temporary \Cyclus servers on the back-end. These servers are hosted by
the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of
Wisconsin-Madison. Whenever a pull request is created, Polyphemus performs
the following actions:

>>>>

\emph{Continuous integration (CI)} is the idea that software should be tested and validated
as it is being developed, rather than as a final stage in a longer development
cycle.  Under \gls{CI}, every pull request (proposed code change) is tested independently immediately after
it is proposed. Such tests are run on all officially supported platforms.
\Cyclus uses a \gls{CI} platform called Polyphemus
\cite{scopatz_polyphemus_2014}. Polyphemus serves as an intermediary between GitHub pull requests on the front-end
and temporary \Cyclus servers on the back-end. These servers are hosted by
the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of
Wisconsin-Madison. Whenever a pull request is created, Polyphemus performs
the following actions:
